MSSM-Penn-Pitt - ACC and DLPFC - DREAM - FEATURECOUNTS - GRCh38 - CQN - Model Selection

### 2020-04-14 cmc-rnaseq-de/MSSM-Penn-Pitt_ACC_DLPFC_FEATURECOUNTS_GRCh38_CQN_Sparse.Rmd
save to testing folder

knit2synapse::createAndKnitToFolderEntity(file = "./cmc-rnaseq-de/MSSM-Penn-Pitt_ACC_DLPFC_FEATURECOUNTS_GRCh38_CQN_Sparse.Rmd",
                                 parentId ="syn21435176",
                                 folderName = "MSSM-Penn-Pitt - ACC and DLPFC - DREAM - FEATURECOUNTS - GRCh38 - CQN")
```

@@

# Github link
thisRepo <- getRepo(repository = "kelshmo/analysis", ref="branch", refName='add-dream')
thisFile <- getPermlink(repository = thisRepo, repositoryPath=paste0('cmc-rnaseq-de/',thisFileName))
```
### Data download
#### Obtain count matrix and metadata from synapse.
```{r download.data, cache=TRUE}
downloadFile <- function(id){
  fread(synGet(id)$path, data.table = F)
}
downloadFile_version <- function(id , version){
  fread(synGet(id, version = version)$path, data.table = F)
}
# Download reprocessed counts
counts = 'syn21867938'
ALL_USED_IDs = counts
counts = downloadFile(counts) %>% data.frame()
counts$Chr <- NULL
counts$Start <- NULL
counts$End <- NULL
counts$Strand <- NULL

@@

# Code
CODE <- Folder(name = "MSSM-Penn-Pitt - ACC and DLPFC - DREAM - FEATURECOUNTS - GRCh38 - CQN", parentId = parentId)
CODE <- synStore(CODE)

>>>>

knit2synapse::createAndKnitToFolderEntity(file = "./cmc-rnaseq-de/MSSM-Penn-Pitt_ACC_DLPFC_FEATURECOUNTS_GRCh38_CQN_Sparse.Rmd",
                                 parentId ="syn21435176",
                                 folderName = "test mvBIC - MSSM-Penn-Pitt - ACC and DLPFC - DREAM - FEATURECOUNTS - GRCh38 - CQN")
```

@@

# Github link
thisRepo <- getRepo(repository = "kelshmo/analysis", ref="branch", refName='master')
thisFile <- getPermlink(repository = thisRepo, repositoryPath=paste0('cmc-rnaseq-de/',thisFileName))
```
### Data download
#### Obtain count matrix and metadata from synapse.
```{r download.data, cache=TRUE}
downloadFile <- function(id){
  fread(synGet(id)$path, data.table = F)
}
downloadFile_version <- function(id , version){
  fread(synGet(id, version = version)$path, data.table = F)
}
# Download reprocessed counts
counts = 'syn21867938'
ALL_USED_IDs = counts
counts = downloadFile(counts) %>% data.frame()
counts$Chr <- NULL
counts$Start <- NULL
counts$End <- NULL
counts$Strand <- NULL

@@

# Code
CODE <- Folder(name = "test mvBIC - MSSM-Penn-Pitt - ACC and DLPFC - DREAM - FEATURECOUNTS - GRCh38 - CQN", parentId = parentId)
CODE <- synStore(CODE)
